---
title: "Mesocarnivore community temporal analyses: Data into temporal data all seasons" ## name of your project
author: "Julie Louvrier, Aimara Planillo, Stephanie Kramer-Schadt"                     ## your name(s)
date: "`r Sys.Date()`"                  ## current date
output:
  rmdformats::readthedown:
    code_folding: hide                  ## hide or show code by default?
    toc_depth: 3                        ## 3-level TOC
---

```{r setup, include=FALSE}
## You can ignore this chunk in most cases
## If you want to modify chunk options, you can do it here for all chunks or
## add the options in the repsective chunk header, e.g. `{r, message = FALSE}`
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE,
                      fig.width = 9, fig.height = 6, dpi = 500, 
                      retina = 1, fig.showtext = TRUE)
```

* **Research question:do urban mesocarnivores experience temporal partitioning in gardens? **
* **Study area: Berlin fall 2018, spring 2019, fall 2019, spring 2020, fall 2020**
* **Data: all seasons ** 


# Setup
### Packages

```{r packages}
## for non-CRAN packages please keep install instruction
## but commented so it is not run each time, e.g.
# devtools::install_github("EcoDynIZW/template")

## libraries used in this script
## please add ALL LIBRARIES NEEDED HERE
## please remove libraries from the list that are not needed anymore 
## at a later stage
#### load required libraries ####
package.list=c("camtrapR",
               #"camtrapRdeluxe",
               "dplyr",
               "evaluate",
               "gdata",
               "here",
               "janitor",
               "lubridate",
               "maptools",
               "optimbase",
               "plyr",
               "raster",
               "readxl",
               #"rgdal",
               #"rgeos",
               #"rjags",
               "rlecuyer",
               #"sf",
               "showtext",
               "snowfall",
               #"sp",
               "stringr",
               "tidyverse"
               )

for (package in package.list) {
  if (!require(package, character.only=T, quietly=T)) {
    install.packages(package)
    library(package, character.only=T)
  }
}

```

### Workspace
```{r}
WorkDir <- here::here()


procdata_wd <- file.path(WorkDir, "output/data-proc/temporal_processed_data")
plots_wd <- file.path(WorkDir, "plots/temp")
```

### Loading data

```{r data}
##Camera Traps detection histories
CT_act_date_formated_delta30 <- readRDS( here::here("output", "data-proc", "all_seasons", "Louvrier_2021_JAE_UrbanMesocarnivores_Camera_detections_Dryad2021_11_05.RDS"))

#loading the environmental variables and using only the user IDs that are within the cov table
stacked_raster_values_and_garden_CT_all_seasons_no_nas <- readRDS( here::here("output", "data-proc", "all_seasons", "Louvrier_2021_JAE_UrbanMesocarnivores_Covariates_cameras_Dryad2021_10_29.RDS"))

```   

#calculate the time intervals between last detections of the primary species (A) and first detection of the secondary species (B) 

```{r}

#taking out pictures between 6 am and 6pm (Medium night = MN (after trying long nights and short nights))
CT_act_MN <- CT_act_date_formated_delta30
CT_act_MN$Time <- strptime(CT_act_MN$Time, "%H:%M:%S") #ugh somehow it adss the date of today

#extract the hours after 6pm
MN_1 <- CT_act_MN %>% dplyr::filter(Time >= paste0(gsub("-", "-", Sys.Date())," 18:00:00") 
                                & Time <= paste0(gsub("-", "-", Sys.Date())," 24:00:00"))

#extract the hours before 6 am
MN_2 <- CT_act_MN %>% dplyr::filter(Time >= paste0(gsub("-", "-", Sys.Date())," 00:00:00") 
                                & Time <= paste0(gsub("-", "-", Sys.Date())," 06:00:00"))

#combined bothdatasets
medium_night <- rbind(MN_1,MN_2)

#saving the output
saveRDS(medium_night, file = here::here("output", "data-proc", "temporal_processed_data", paste0("medium_night",gsub("-", "_", Sys.Date()),".RDS")))

# !!!!! if you have issues with camtrapRdelux !!!!!

# install.packages("remotes")
# remotes::install_github("carlopacioni/camtrapRdeluxe")
# 
# unzip("~/Downloads/camtrapRdeluxe-master.zip")
# file.rename("camtrapRdeluxe-master", "camtrapRdeluxe")
# system("R CMD build camtrapRdeluxe")
# system('defaults write org.R-project.R force.LANG en_US.UTF-8') #LINE TO RUN IN CASE OF ERROR AGAIN

```

##Calculate the temporal difference between each species 
```{r}
#a bit of formating 
d1_interest <- medium_night
d1_interest$Species <- as.factor(d1_interest$Species)
d1_interest$Station <- as.integer(d1_interest$Station)
d1_interest <- as.data.frame(d1_interest)

#extracting the ids of the CT that detected both racoons and cats
id_CT <- unique(d1_interest$Station)

#list of species of interest 
species_interest <- c("cat", "Waschbär","Rotfuchs", "Marder_(Baum-und_Steinmarder)")

calculate_delta <- function(species)
  {
  #empty list 
  delta_species <- list(0)
  ###loop starts here
  
  for(j in id_CT)
    {
    k = which(id_CT == j)
    #take the CT by its id 
    B <- d1_interest %>% filter(Station == j)
  
    #order it by date and time
    B_ordered <- B %>% arrange(DateTimeOriginal)

    #delta is going to contain the calculated difference of time between species A and B for each row of the detections of the CT
    #but only if the two species from row i and i+1 are in the specific order
    #if the combination of the species names between the row i and i + 1 is equal to the names of the species of interest     stuck togetehr then we calcutalte difftime between the two lines,  otherwise, no
  
    delta <- rep(NA, nrow(B_ordered))
    for(i in 1: (nrow(B_ordered)))
      {
      if (paste(B_ordered[c(i:(i+1)),"Species"], collapse ="") == paste(species, collapse=""))
        { 
        diff <- difftime(B_ordered[i,"DateTimeOriginal"], B_ordered[i+1,"DateTimeOriginal"])
        if (diff < - 12)
          { 
          delta[i] <- 0 #if the time difference is more thant 12 hours then we set it back to zero because it means too                             much time has spent
          }
        if (diff >= -12)
          {
          delta[i] <- diff
          }
        }
      }
  
    delta_species[[k]] <- delta
    names(delta_species)[k] <- as.character(j)
  
    }
  return(delta_species)

  }

##selecting the species cat and raccoon
species = c(species_interest[1],species_interest[2])
delta_cat_raccoon <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficient.... sorry
#putting this in a dataframe 
df_time_diff_cat_raccoon = plyr::ldply(delta_cat_raccoon, rbind)

##selecting the species raccoon and cat
species = c(species_interest[2],species_interest[1])
delta_raccoon_cat <- calculate_delta(species) 
#putting this in a dataframe 
df_time_diff_raccoon_cat = plyr::ldply(delta_raccoon_cat, rbind)

##selecting the species cat and fox
species = c(species_interest[1],species_interest[3])
delta_cat_fox <- calculate_delta(species)
#putting this in a dataframe 
df_time_diff_cat_fox = plyr::ldply(delta_cat_fox, rbind)

##selecting the species fox and cat
species = c(species_interest[3],species_interest[1])
delta_fox_cat <- calculate_delta(species)
#putting this in a dataframe 
df_time_diff_fox_cat = plyr::ldply(delta_fox_cat, rbind)

##selecting the species cat and marten
species = c(species_interest[1],species_interest[4])
delta_cat_marten <- calculate_delta(species)
#putting this in a dataframe 
df_time_diff_cat_marten = plyr::ldply(delta_cat_marten, rbind)

##selecting the species marten and cat
species = c(species_interest[4],species_interest[1])
delta_marten_cat <- calculate_delta(species)
#putting this in a dataframe 
df_time_diff_marten_cat = plyr::ldply(delta_marten_cat, rbind)

##selecting the species cat and cat
species = c(species_interest[1],species_interest[1])
delta_cat_cat <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_cat_cat = plyr::ldply(delta_cat_cat, rbind)



##selecting the species fox and raccoon
species = c(species_interest[3],species_interest[2])
delta_fox_raccoon <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_fox_raccoon = plyr::ldply(delta_fox_raccoon, rbind)

##selecting the species raccoon and fox
species = c(species_interest[2],species_interest[3])
delta_raccoon_fox <- calculate_delta(species) 
#putting this in a dataframe 
df_time_diff_raccoon_fox = plyr::ldply(delta_raccoon_fox, rbind)

##selecting the species fox and marten
species = c(species_interest[3],species_interest[4])
delta_fox_marten <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_fox_marten = plyr::ldply(delta_fox_marten, rbind)

##selecting the species marten and fox
species = c(species_interest[4],species_interest[3])
delta_marten_fox <- calculate_delta(species) 
#putting this in a dataframe 
df_time_diff_marten_fox = plyr::ldply(delta_marten_fox, rbind)

##selecting the species fox and fox
species = c(species_interest[3],species_interest[3])
delta_fox_fox <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_fox_fox = plyr::ldply(delta_fox_fox, rbind)



#selecting the species raccoon and marten
species = c(species_interest[2],species_interest[4])
delta_raccon_marten <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_raccoon_marten = plyr::ldply(delta_raccon_marten, rbind)

##selecting the species marten and raccoon
species = c(species_interest[4],species_interest[2])
delta_marten_raccoon <- calculate_delta(species) 
#putting this in a dataframe 
df_time_diff_marten_raccoon = plyr::ldply(delta_marten_raccoon, rbind)

##selecting the species raccoon and raccoon
species = c(species_interest[2],species_interest[2])
delta_raccoon_raccoon <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_raccoon_raccoon = plyr::ldply(delta_raccoon_raccoon, rbind)


##selecting the species marten and marten
species = c(species_interest[4],species_interest[4])
delta_marten_marten <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_marten_marten = plyr::ldply(delta_marten_marten, rbind)


average_diff_cat_raccoon_id <- df_time_diff_cat_raccoon %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_cat_raccoon[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_raccoon_cat_id <- df_time_diff_raccoon_cat %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_raccoon_cat[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_cat_fox_id <- df_time_diff_cat_fox %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_cat_fox[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_fox_cat_id <- df_time_diff_fox_cat %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_fox_cat[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_cat_marten_id <- df_time_diff_cat_marten %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_cat_marten[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_marten_cat_id <- df_time_diff_marten_cat %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_marten_cat[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_cat_cat_id <- df_time_diff_cat_cat %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_cat_cat[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column



average_diff_fox_raccoon_id <- df_time_diff_fox_raccoon %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_fox_raccoon[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_raccoon_fox_id <- df_time_diff_raccoon_fox %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_raccoon_fox[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_fox_marten_id <- df_time_diff_fox_marten %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_fox_marten[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_marten_fox_id <- df_time_diff_marten_fox %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_marten_fox[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_fox_fox_id <- df_time_diff_fox_fox %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_fox_fox[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column




average_diff_raccoon_marten_id <- df_time_diff_raccoon_marten %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_raccoon_marten[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_marten_raccoon_id <- df_time_diff_marten_raccoon %>%
                              mutate(User_uid = as.numeric(.id)) %>%
                              mutate(mean = rowMeans(df_time_diff_marten_raccoon[,-1], na.rm = T)) %>% #rowmeans
                              dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_raccoon_raccoon_id <- df_time_diff_raccoon_raccoon %>%
                            mutate(User_uid = as.numeric(.id)) %>%
                            mutate(mean = rowMeans(df_time_diff_raccoon_raccoon[,-1], na.rm = T)) %>% #rowmeans
                            dplyr::select(User_uid, mean) #keeping only the mean and the id column



average_diff_marten_marten_id <- df_time_diff_marten_marten %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_marten_marten[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

```

## joining the environmental covariates

```{r}

# joining both tables
# resulting is 667 CTs (instead of 671 for use and detect-non detect due to the fact that we selected the pictures only during the night and 4 CTs got taken out)

# cat
average_diff_cat_raccoon_id_covenv <- dplyr::inner_join(average_diff_cat_raccoon_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)

average_diff_raccoon_cat_id_covenv <- dplyr::inner_join(average_diff_raccoon_cat_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)

average_diff_cat_fox_id_covenv <- dplyr::inner_join(average_diff_cat_fox_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)

average_diff_fox_cat_id_covenv <- dplyr::inner_join(average_diff_fox_cat_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)

average_diff_cat_marten_id_covenv <- dplyr::inner_join(average_diff_cat_marten_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)

average_diff_marten_cat_id_covenv <- dplyr::inner_join(average_diff_marten_cat_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)

average_diff_cat_cat_id_covenv <- dplyr::inner_join(average_diff_cat_cat_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)

#fox
average_diff_fox_raccoon_id_covenv <- dplyr::inner_join(average_diff_fox_raccoon_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)

average_diff_raccoon_fox_id_covenv <- dplyr::inner_join(average_diff_raccoon_fox_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)

average_diff_fox_marten_id_covenv <- dplyr::inner_join(average_diff_fox_marten_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)

average_diff_marten_fox_id_covenv <- dplyr::inner_join(average_diff_marten_fox_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)

average_diff_fox_fox_id_covenv <- dplyr::inner_join(average_diff_fox_fox_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)


#raccoon
average_diff_raccoon_marten_id_covenv <- dplyr::inner_join(average_diff_raccoon_marten_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)

average_diff_marten_raccoon_id_covenv <- dplyr::inner_join(average_diff_marten_raccoon_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)

average_diff_raccoon_raccoon_id_covenv <- dplyr::inner_join(average_diff_raccoon_raccoon_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)


#marten
average_diff_marten_marten_id_covenv <- dplyr::inner_join(average_diff_marten_marten_id, stacked_raster_values_and_garden_CT_all_seasons_no_nas)




#saving all of that
saveRDS(average_diff_cat_raccoon_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_cat_raccoon_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))

saveRDS(average_diff_raccoon_cat_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_raccoon_cat_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))

saveRDS(average_diff_cat_fox_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_cat_fox_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))

saveRDS(average_diff_fox_cat_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_fox_cat_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))

saveRDS(average_diff_cat_marten_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_cat_marten_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))

saveRDS(average_diff_marten_cat_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_marten_cat_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))

saveRDS(average_diff_cat_cat_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_cat_cat_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))


saveRDS(average_diff_fox_raccoon_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_fox_raccoon_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))

saveRDS(average_diff_raccoon_fox_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_raccoon_fox_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))

saveRDS(average_diff_fox_marten_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_fox_marten_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))

saveRDS(average_diff_marten_fox_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_marten_fox_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))

saveRDS(average_diff_fox_fox_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_fox_fox_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))


saveRDS(average_diff_raccoon_marten_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_raccoon_marten_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))

saveRDS(average_diff_marten_raccoon_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_marten_raccoon_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))

saveRDS(average_diff_raccoon_raccoon_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_raccoon_raccoon_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))

saveRDS(average_diff_marten_marten_id_covenv, file = here::here("output", "data-proc", "temporal_processed_data", paste0("average_diff_marten_marten_id_covenv",gsub("-", "_", Sys.Date()),".RDS")))


```



***

<details><summary>Session Info</summary>

```{r sessionInfo}
## DO NOT REMOVE!
## We store the settings of your computer and the current versions of the
## packages used to allow for reproducibility
Sys.time()
#git2r::repository() ## uncomment if you are using GitHub
sessionInfo()
```

</details>
