---
title: "Plots_JSDMs"
author: "Aimara Planillo"
date: "15/04/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Plotting the JSDMs results

```{r packages and workspace}
source(paste0(getwd(), "/3_scripts/source_file_lib.R"))
source(paste0(getwd(), "/3_scripts/source_file_wd.R"))
```


### Load data
```{r}
# Detection
det_file <- list.files(det_results_wd, pattern = "ModelFrame")
det_betas <- read.csv(file.path(det_results_wd, det_file))

# Use intensity
use_file <- list.files(use_results_wd, pattern = "ModelFrame")
use_betas <- read.csv(file.path(use_results_wd, use_file))

# Nocturnality
noct_file <- list.files(nocturnality2_results_wd, pattern = "ModelFrame")
noct_betas <- read.csv(file.path(nocturnality2_results_wd, noct_file))
```


### Detection forest plot
```{r}
# Correct variable name and set variables in the correct order for plotting
det_ModelFrame <- det_betas %>%
  mutate(Variable = case_when(
    Variable == "Dist_B" ~ "Dist_CityBorder",
    TRUE ~ as.character(Variable))) %>%
  mutate(Variable = fct_relevel(Variable, c("Intercept",  "Spring", "Covid",
              "No_compost", "Open_compost", "Garden_size", "Local_tree_cover", "Fence_height",
              "Human_population", "Impervious_surface", "Noise", "Tree_cover", "Dist_CityBorder", 
               "Cat"))) %>%
  mutate(Variable = fct_rev(Variable))
 
det_ModelFrame$Variable

# variables with CRI not overlapping 0
det_ModelFrame <- det_ModelFrame %>%
  mutate(significant = case_when(
    CI_low < 0 & CI_high < 0 ~ "Yes",
    CI_low > 0 & CI_high > 0 ~ "Yes", 
    TRUE ~ "No")) 


# Remove intercept not to plot it
det_ModelFrame <- det_ModelFrame %>% 
  filter(Variable != "Intercept")

# Plot
zp1 <- ggplot(det_ModelFrame, aes(group = Species, colour = Species)) + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
  geom_linerange(aes(x = Variable, ymin = CI_low,
                                ymax = CI_high, fill = significant),
                            lwd = 0.8, position = position_dodge(width = 1.2/2)) + 
  geom_linerange(aes(x = Variable, ymin = Q_25,
                                ymax = Q_75, fill = significant),
                            lwd = 1.5, position = position_dodge(width = 1.2/2)) + 
  geom_pointrange(aes(x = Variable, y = Coefficient, ymin = Q_25,
                                 ymax = Q_75, fill = significant),
                             lwd = 1/2, shape = 21, position = position_dodge(width = 1.2/2)) +
  scale_fill_manual(values = c("White", "black"))+
  # scale_y_continuous(limits = c(-5, 3)) +
  coord_flip(ylim=c(-2, 1)) + 
  scale_colour_viridis_d(option = "viridis", begin = 0.1, end = 0.9, 
                         guide = guide_legend(reverse = TRUE)) +
  theme(
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_blank(), 
    axis.line = element_line(colour = "black"), 
    axis.text = element_text(size = 12), 
    axis.title = element_text(size = 14, face = "bold")) +
    ggtitle("Detection of Urban Mesocarnivores")


zp1

ggsave(plot = zp1, paste0(plots_wd, "/DET_betacoefs_5seasons.png"), 
       width = 9, height = 8, dpi = 600)
```

## Add boxes to plot
```{r}
# make transparent zp1 plot and remove title
zp1 <- zp1 +
  theme(plot.background = element_rect(fill = "transparent", colour = NA), 
        panel.grid = element_line(colour = "transparent")) +
  ggtitle("")
  

# creating just a plot with the boxes and text to overlap
zp2 <- 
ggplot(det_ModelFrame, aes(y = Variable, x = CI_high)) + 
  geom_blank() +
  theme(
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_blank(), 
    # axis.line = element_line(colour = "black"),
    # axis.text = element_text(),
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(), 
    plot.margin = unit(c(1, 3, 2, 1), "cm")) + # add margin for the other plot 
  annotate("rect", xmin = -4, xmax = 8, ymin = 0.6, ymax = 1.4,
           fill = "red", alpha = .1) +
  annotate("text", label = "Cats", fontface = "italic", size = 5,
           x = -3.5, y = 0.6, vjust = -0.5, hjust = 0) +
  annotate("rect", xmin = -4, xmax = 8, ymin = 1.6, ymax = 7.2,
           fill = "grey", alpha = .1) +
  annotate("text", label = "Urban", fontface = "italic", size = 5,
           x = -3.5, y = 4,5, vjust = -0.5, hjust = 0) +
  annotate("rect", xmin = -4, xmax = 8, ymin = 7.4, ymax = 12.8,
           fill = "darkgreen", alpha = .1) +
  annotate("text", label = "Garden", fontface = "italic", size = 5,
           x = -3.5, y = 10, vjust = -0.5, hjust = 0) +
  annotate("rect", xmin = -4, xmax = 8, ymin = 13, ymax = 15,
           fill = "darkblue", alpha = .1) +
  annotate("text", label = "Season/Covid", fontface = "italic", size = 5,
           x = -3.5, y = 13.8, vjust = -0.5, hjust = 0)
  
  
# transform into grob object to overlap
zp1_grob <- ggplotGrob(zp1)

# Plot on top of each other
combined_plot <- zp2 + annotation_custom(grob = zp1_grob, 
                    xmin = -2.3, xmax = 10, 
                       ymin = -0.8, ymax = 16)

# save
ggsave(plot = combined_plot, paste0(plots_wd, "/DET_betacoefs_5seasons_boxes.png"), 
       width = 9, height = 8, dpi = 600)
```


### USE intensity forest plot
```{r}
# Correct variable name and set variables in the correct order for plotting
use_ModelFrame <- use_betas %>%
  mutate(Variable = case_when(
    Variable == "Dist_B" ~ "Dist_CityBorder",
    TRUE ~ as.character(Variable))) %>%
  mutate(Variable = fct_relevel(Variable, c("Intercept",  "Spring", "Covid",
              "No_compost", "Open_compost", "Garden_size", "Local_tree_cover", "Fence_height",
              "Human_population", "Impervious_surface", "Noise", "Tree_cover", "Dist_CityBorder", 
               "Cat"))) %>%
  mutate(Variable = fct_rev(Variable))

use_ModelFrame$Variable
 
# variables with CRI not overlapping 0
use_ModelFrame <- use_ModelFrame %>%
  mutate(significant = case_when(
    CI_low < 0 & CI_high < 0 ~ "Yes",
    CI_low > 0 & CI_high > 0 ~ "Yes", 
    TRUE ~ "No")) 


# Remove intercept not to plot it
use_ModelFrame <- use_ModelFrame %>% 
  filter(Variable != "Intercept")

# Plot
zp1_use <- ggplot(use_ModelFrame, aes(group = Species, colour = Species)) + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
  geom_linerange(aes(x = Variable, ymin = CI_low,
                                ymax = CI_high, fill = significant),
                            lwd = 0.8, position = position_dodge(width = 1.2/2)) + 
  geom_linerange(aes(x = Variable, ymin = Q_25,
                                ymax = Q_75, fill = significant),
                            lwd = 1.5, position = position_dodge(width = 1.2/2)) + 
  geom_pointrange(aes(x = Variable, y = Coefficient, ymin = Q_25,
                                 ymax = Q_75, fill = significant),
                             lwd = 1/2, shape = 21, position = position_dodge(width = 1.2/2)) +
  scale_fill_manual(values = c("White", "black"))+
  # scale_y_continuous(limits = c(-5, 3)) +
  coord_flip(ylim=c(-1, 1)) + 
  scale_colour_viridis_d(option = "viridis", begin = 0.1, end = 0.9, 
                         guide = guide_legend(reverse = TRUE)) +
  theme(
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_blank(), 
    axis.line = element_line(colour = "black"), 
    axis.text = element_text(size = 12), 
    axis.title = element_text(size = 14, face = "bold")) +
    ggtitle("Use intensity by Urban Mesocarnivores")


zp1_use

ggsave(plot = zp1_use, paste0(plots_wd, "/USE_betacoefs_5seasons.png"), 
       width = 9, height = 8, dpi = 600)
```

## Add boxes to plot
```{r}
# make transparent zp1 plot and remove title
zp1_use <- zp1_use +
  theme(plot.background = element_rect(fill = "transparent", colour = NA), 
        panel.grid = element_line(colour = "transparent")) +
  ggtitle("")
  

# creating just a plot with the boxes and text to overlap
zp2_use <- 
ggplot(use_ModelFrame, aes(y = Variable, x = CI_high)) + 
  geom_blank() +
  theme(
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_blank(), 
    # axis.line = element_line(colour = "black"),
    # axis.text = element_text(),
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(), 
    plot.margin = unit(c(1, 3, 2, 1), "cm")) + # add margin for the other plot 
  annotate("rect", xmin = -4, xmax = 8, ymin = 0.6, ymax = 1.4,
           fill = "red", alpha = .1) +
  annotate("text", label = "Cats", fontface = "italic", size = 5,
           x = -3.5, y = 0.6, vjust = -0.5, hjust = 0) +
  annotate("rect", xmin = -4, xmax = 8, ymin = 1.6, ymax = 7.2,
           fill = "grey", alpha = .1) +
  annotate("text", label = "Urban", fontface = "italic", size = 5,
           x = -3.5, y = 4,5, vjust = -0.5, hjust = 0) +
  annotate("rect", xmin = -4, xmax = 8, ymin = 7.4, ymax = 12.8,
           fill = "darkgreen", alpha = .1) +
  annotate("text", label = "Garden", fontface = "italic", size = 5,
           x = -3.5, y = 10, vjust = -0.5, hjust = 0) +
  annotate("rect", xmin = -4, xmax = 8, ymin = 13, ymax = 15,
           fill = "darkblue", alpha = .1) +
  annotate("text", label = "Season/Covid", fontface = "italic", size = 5,
           x = -3.5, y = 13.8, vjust = -0.5, hjust = 0)
  
  
# transform into grob object to overlap
zp1_use_grob <- ggplotGrob(zp1_use)

# Plot on top of each other
combined_use_plot <- zp2 + annotation_custom(grob = zp1_use_grob, 
                    xmin = -2.3, xmax = 10, 
                       ymin = -0.8, ymax = 16)

# save
ggsave(plot = combined_use_plot, paste0(plots_wd, "/USE_betacoefs_5seasons_boxes.png"), 
       width = 9, height = 8, dpi = 600)
```


### NOCTURNALITY forest plot
```{r}
# Correct variable name and set variables in the correct order for plotting
noct_ModelFrame <- noct_betas %>%
  mutate(Variable = case_when(
    Variable == "Dist_B" ~ "Dist_CityBorder",
    TRUE ~ as.character(Variable))) %>%
  mutate(Variable = fct_relevel(Variable, c("Intercept",  "Spring", "Covid",
              "No_compost", "Open_compost", "Garden_size", "Local_tree_cover", "Fence_height",
              "Human_population", "Impervious_surface", "Noise", "Tree_cover", "Dist_CityBorder", 
               "Cat"))) %>%
  mutate(Variable = fct_rev(Variable))

noct_ModelFrame$Variable
 
# variables with CRI not overlapping 0
noct_ModelFrame <- noct_ModelFrame %>%
  mutate(significant = case_when(
    CI_low < 0 & CI_high < 0 ~ "Yes",
    CI_low > 0 & CI_high > 0 ~ "Yes", 
    TRUE ~ "No")) 


# Remove intercept not to plot it
noct_ModelFrame <- noct_ModelFrame %>% 
  filter(Variable != "Intercept")

# Plot
zp1_noct <- ggplot(noct_ModelFrame, aes(group = Species, colour = Species)) + 
  geom_hline(yintercept = 0, colour = gray(1/2), lty = 2) + 
  geom_linerange(aes(x = Variable, ymin = CI_low,
                                ymax = CI_high, fill = significant),
                            lwd = 0.8, position = position_dodge(width = 1.2/2)) + 
  geom_linerange(aes(x = Variable, ymin = Q_25,
                                ymax = Q_75, fill = significant),
                            lwd = 1.5, position = position_dodge(width = 1.2/2)) + 
  geom_pointrange(aes(x = Variable, y = Coefficient, ymin = Q_25,
                                 ymax = Q_75, fill = significant),
                             lwd = 1/2, shape = 21, position = position_dodge(width = 1.2/2)) +
  scale_fill_manual(values = c("White", "black"))+
  # scale_y_continuous(limits = c(-5, 3)) +
  coord_flip(ylim=c(-1, 1)) + 
  scale_colour_viridis_d(option = "viridis", begin = 0.1, end = 0.9, 
                         guide = guide_legend(reverse = TRUE)) +
  theme(
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_blank(), 
    axis.line = element_line(colour = "black"), 
    axis.text = element_text(size = 12), 
    axis.title = element_text(size = 14, face = "bold")) +
    ggtitle("Nocturnality of Urban Mesocarnivores")


zp1_noct

ggsave(plot = zp1_noct, paste0(plots_wd, "/NOCT_betacoefs_5seasons.png"), 
       width = 9, height = 8, dpi = 600)
```

## Add boxes to plot
```{r}
# make transparent zp1 plot and remove title
zp1_noct <- zp1_noct +
  theme(plot.background = element_rect(fill = "transparent", colour = NA), 
        panel.grid = element_line(colour = "transparent")) +
  ggtitle("")
  

# creating just a plot with the boxes and text to overlap
zp2_noct <- 
ggplot(noct_ModelFrame, aes(y = Variable, x = CI_high)) + 
  geom_blank() +
  theme(
    panel.background = element_rect(fill = NA),
    panel.grid.major = element_blank(), 
    # axis.line = element_line(colour = "black"),
    # axis.text = element_text(),
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(), 
    plot.margin = unit(c(1, 3, 2, 1), "cm")) + # add margin for the other plot 
  annotate("rect", xmin = -4, xmax = 8, ymin = 0.6, ymax = 1.4,
           fill = "red", alpha = .1) +
  annotate("text", label = "Cats", fontface = "italic", size = 5,
           x = -3.5, y = 0.6, vjust = -0.5, hjust = 0) +
  annotate("rect", xmin = -4, xmax = 8, ymin = 1.6, ymax = 7.2,
           fill = "grey", alpha = .1) +
  annotate("text", label = "Urban", fontface = "italic", size = 5,
           x = -3.5, y = 4,5, vjust = -0.5, hjust = 0) +
  annotate("rect", xmin = -4, xmax = 8, ymin = 7.4, ymax = 12.8,
           fill = "darkgreen", alpha = .1) +
  annotate("text", label = "Garden", fontface = "italic", size = 5,
           x = -3.5, y = 10, vjust = -0.5, hjust = 0) +
  annotate("rect", xmin = -4, xmax = 8, ymin = 13, ymax = 15,
           fill = "darkblue", alpha = .1) +
  annotate("text", label = "Season/Covid", fontface = "italic", size = 5,
           x = -3.5, y = 13.8, vjust = -0.5, hjust = 0)
  
  
# transform into grob object to overlap
zp1_noct_grob <- ggplotGrob(zp1_noct)

# Plot on top of each other
combined_noct_plot <- zp2_noct + annotation_custom(grob = zp1_noct_grob, 
                    xmin = -2.3, xmax = 10, 
                       ymin = -0.8, ymax = 16)

# save
ggsave(plot = combined_noct_plot, paste0(plots_wd, "/NOCT_betacoefs_5seasons_boxes.png"), 
       width = 9, height = 8, dpi = 600)
```





# Variance partitioning

We are going to plot it manually, so we can plot species names and chosen colors.

### Load variance partitioning data
```{r}
# Varpart data

# Detection
VP_det <- readRDS(paste0(det_results_wd, "/Varpart_DET_5seasons.rds"))
VP_det  

# Use intensity
VP_use <- readRDS(paste0(use_results_wd, "/Varpart_USE_5seasons.rds"))
VP_use  

# Nocturnality
VP_noct <- readRDS(paste0(nocturnality2_results_wd, "/Varpart_NOCT_5seasons.rds"))
VP_noct
```



### Detection model var part
```{r, message=FALSE}
# Extract the values for the manual plot
VPdet_vals <- as.data.frame(VP_det$vals)
ncol(VPdet_vals)
mean_vpdet <- as.data.frame(rowSums(VPdet_vals[1:3])/ncol(VPdet_vals[1:3]))
colnames(mean_vpdet) <- "mean"
mean_vpdet <- mean_vpdet %>% 
  rownames_to_column("variable") %>% 
  mutate(percent = round(mean * 100,2), 
         variable = factor(variable, levels = c("Random: site", "covid", "season", "garden",  "urban", "cats")))  
mean_vpdet

# set species names
my_species <- c("Red_fox", "Raccoon", "Marten")

colnames(VPdet_vals) <- my_species
VPdet_vals$variable <- row.names(VPdet_vals)

# Transform the dataframe into the required format
VPdet_toplot<- melt(VPdet_vals, id.vars = "variable")
colnames(VPdet_toplot)[2] <- "species"
# Give the order (top down) to the levels of the factor to plot
VPdet_toplot$variable <- factor(VPdet_toplot$variable, levels = c("Random: site", "covid", "season", "garden",  "urban", "cats"))

head(VPdet_toplot)
tail(VPdet_toplot)

plot(VPdet_toplot$value ~ VPdet_toplot$variable)

# write.csv(VPdet_toplot, paste0(det_results_wd, "/VPdet_toplot"), row.names = FALSE)
# VPdet_toplot <- read.csv(paste0(det_results_wd, "/VPdet_toplot"))

mean_vpdet[VPdet_toplot$variable[1]]
mean_vpdet[VPdet_toplot$variable[6]]

varpartplot <- ggplot(VPdet_toplot, aes(x = species, y = value, fill=variable)) +
  geom_bar(stat='identity', colour = "grey40", alpha = 0.3) +
  scale_fill_manual(values=alpha(c("lightyellow", "darkorchid4", "darkblue", "darkgreen", "grey", "red"), 0.5),
                    name = "Variable type", 
                    labels=c(paste0("Random factor\n(mean = ", 
                                       mean_vpdet$percent[mean_vpdet$variable == VPdet_toplot$variable[6]], ")"),
                             paste0("Covid\n(mean = ", 
                                       mean_vpdet$percent[mean_vpdet$variable == "covid"], ")"), 
                                paste0("Season\n(mean = ", 
                                       mean_vpdet$percent[mean_vpdet$variable == "season"], ")"), 
                                paste0("Garden\n(mean = ", 
                                       mean_vpdet$percent[mean_vpdet$variable == "garden"], ")"),
                                paste0("Urban\n(mean = ", 
                                       mean_vpdet$percent[mean_vpdet$variable == "urban"], ")"),
                               paste0("Cats\n(mean = ", 
                                       mean_vpdet$percent[mean_vpdet$variable == "cats"], ")"))) +
  labs(#title = "Variance Partitioning", 
       x = "\nCarnivore Species", 
       y = "Variance partitioning (%)\n", col = "black") +
  scale_y_continuous(limits = c(0,1.01), expand = c(0, 0)) +
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0, 
                                   size=10, colour = "black"),
        axis.text.y = element_text(colour = "black", size = 10),
        axis.title.y = element_text(hjust = 0.5, vjust = 1.5),
        # legend.position = "right", 
        # legend.title = element_blank(), 
        legend.key.height = unit(1.5, "lines"),
        # legend.key.width = unit(1.5, "lines"), 
        # legend.spacing.y = unit(-3, 'cm'),
        # legend.text=element_text(size=10))
  )

varpartplot 

ggsave(paste0(plots_wd, "/DET_Varpart_5seasons.png"), plot = varpartplot, 
       dpi = 600, width = 6, height = 5)
```

### Use intensity model var part
```{r, message=FALSE}
# Extract the values for the manual plot
VPuse_vals <- as.data.frame(VP_use$vals)
ncol(VPuse_vals)
mean_vpuse <- as.data.frame(rowSums(VPuse_vals[1:3])/ncol(VPuse_vals[1:3]))
colnames(mean_vpuse) <- "mean"
mean_vpuse <- mean_vpuse %>% 
  rownames_to_column("variable") %>% 
  mutate(percent = round(mean * 100,2), 
         variable = factor(variable, levels = c("Random: site", "covid", "season", "garden",  "urban", "cats")))  
mean_vpuse

# set species names
my_species <- c("Red_fox", "Raccoon", "Marten")

colnames(VPuse_vals) <- my_species
VPuse_vals$variable <- row.names(VPuse_vals)

# Transform the dataframe into the required format
VPuse_toplot<- melt(VPuse_vals, id.vars = "variable")
colnames(VPuse_toplot)[2] <- "species"
# Give the order (top down) to the levels of the factor to plot
VPuse_toplot$variable <- factor(VPuse_toplot$variable, levels = c("Random: site", "covid", "season", "garden",  "urban", "cats"))

head(VPuse_toplot)
tail(VPuse_toplot)

plot(VPuse_toplot$value ~ VPuse_toplot$variable)

# write.csv(VPuse_toplot, paste0(use_results_wd, "/VPuse_toplot"), row.names = FALSE)
# VPuse_toplot <- read.csv(paste0(use_results_wd, "/VPuse_toplot"))

mean_vpuse[VPuse_toplot$variable[1]]
mean_vpuse[VPuse_toplot$variable[6]]

varpartplot_use <- ggplot(VPuse_toplot, aes(x = species, y = value, fill=variable)) +
  geom_bar(stat='identity', colour = "grey40", alpha = 0.3) +
  scale_fill_manual(values=alpha(c("lightyellow", "darkorchid4", "darkblue", "darkgreen", "grey", "red"), 0.5),
                    name = "Variable type", 
                    labels=c(paste0("Random factor\n(mean = ", 
                                       mean_vpuse$percent[mean_vpuse$variable == VPuse_toplot$variable[6]], ")"),
                             paste0("Covid\n(mean = ", 
                                       mean_vpuse$percent[mean_vpuse$variable == "covid"], ")"), 
                                paste0("Season\n(mean = ", 
                                       mean_vpuse$percent[mean_vpuse$variable == "season"], ")"), 
                                paste0("Garden\n(mean = ", 
                                       mean_vpuse$percent[mean_vpuse$variable == "garden"], ")"),
                                paste0("Urban\n(mean = ", 
                                       mean_vpuse$percent[mean_vpuse$variable == "urban"], ")"),
                               paste0("Cats\n(mean = ", 
                                       mean_vpuse$percent[mean_vpuse$variable == "cats"], ")"))) +
  labs(#title = "Variance Partitioning", 
       x = "\nCarnivore Species", 
       y = "Variance partitioning (%)\n", col = "black") +
  scale_y_continuous(limits = c(0,1.01), expand = c(0, 0)) +
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0, 
                                   size=10, colour = "black"),
        axis.text.y = element_text(colour = "black", size = 10),
        axis.title.y = element_text(hjust = 0.5, vjust = 1.5),
        # legend.position = "right", 
        # legend.title = element_blank(), 
        legend.key.height = unit(1.5, "lines"),
        # legend.key.width = unit(1.5, "lines"), 
        # legend.spacing.y = unit(-3, 'cm'),
        # legend.text=element_text(size=10))
  )

varpartplot_use

ggsave(paste0(plots_wd, "/USE_Varpart_5seasons.png"), plot = varpartplot_use, 
       dpi = 600, width = 6, height = 5)
```

### Nocturnality model var part
```{r, message=FALSE}
# Extract the values for the manual plot
VPnoct_vals <- as.data.frame(VP_noct$vals)
ncol(VPnoct_vals)
mean_vpnoct <- as.data.frame(rowSums(VPnoct_vals[1:3])/ncol(VPnoct_vals[1:3]))
colnames(mean_vpnoct) <- "mean"
mean_vpnoct <- mean_vpnoct %>% 
  rownames_to_column("variable") %>% 
  mutate(percent = round(mean * 100,2), 
         variable = factor(variable, levels = c("Random: site", "covid", "season", "garden",  "urban", "cats")))  
mean_vpnoct

# set species names
my_species <- c("Red_fox", "Raccoon", "Marten")

colnames(VPnoct_vals) <- my_species
VPnoct_vals$variable <- row.names(VPnoct_vals)

# Transform the dataframe into the required format
VPnoct_toplot<- melt(VPnoct_vals, id.vars = "variable")
colnames(VPnoct_toplot)[2] <- "species"
# Give the order (top down) to the levels of the factor to plot
VPnoct_toplot$variable <- factor(VPnoct_toplot$variable, levels = c("Random: site", "covid", "season", "garden",  "urban", "cats"))

head(VPnoct_toplot)
tail(VPnoct_toplot)

plot(VPnoct_toplot$value ~ VPnoct_toplot$variable)

# write.csv(VPnoct_toplot, paste0(nocturnality2_results_wd, "/VPnoct_toplot"), row.names = FALSE)
# VPnoct_toplot <- read.csv(paste0(nocturnality2_results_wd, "/VPnoct_toplot"))

mean_vpnoct[VPnoct_toplot$variable[1]]
mean_vpnoct[VPnoct_toplot$variable[6]]

varpartplot_noct <- ggplot(VPnoct_toplot, aes(x = species, y = value, fill=variable)) +
  geom_bar(stat='identity', colour = "grey40", alpha = 0.3) +
  scale_fill_manual(values=alpha(c("lightyellow", "darkorchid4", "darkblue", "darkgreen", "grey", "red"), 0.5),
                    name = "Variable type", 
                    labels=c(paste0("Random factor\n(mean = ", 
                                       mean_vpnoct$percent[mean_vpnoct$variable == VPnoct_toplot$variable[6]], ")"),
                             paste0("Covid\n(mean = ", 
                                       mean_vpnoct$percent[mean_vpnoct$variable == "covid"], ")"), 
                                paste0("Season\n(mean = ", 
                                       mean_vpnoct$percent[mean_vpnoct$variable == "season"], ")"), 
                                paste0("Garden\n(mean = ", 
                                       mean_vpnoct$percent[mean_vpnoct$variable == "garden"], ")"),
                                paste0("Urban\n(mean = ", 
                                       mean_vpnoct$percent[mean_vpnoct$variable == "urban"], ")"),
                               paste0("Cats\n(mean = ", 
                                       mean_vpnoct$percent[mean_vpnoct$variable == "cats"], ")"))) +
  labs(#title = "Variance Partitioning", 
       x = "\nCarnivore Species", 
       y = "Variance partitioning (%)\n", col = "black") +
  scale_y_continuous(limits = c(0,1.01), expand = c(0, 0)) +
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), panel.border = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0, 
                                   size=10, colour = "black"),
        axis.text.y = element_text(colour = "black", size = 10),
        axis.title.y = element_text(hjust = 0.5, vjust = 1.5),
        # legend.position = "right", 
        # legend.title = element_blank(), 
        legend.key.height = unit(1.5, "lines"),
        # legend.key.width = unit(1.5, "lines"), 
        # legend.spacing.y = unit(-3, 'cm'),
        # legend.text=element_text(size=10))
  )

varpartplot_noct

ggsave(paste0(plots_wd, "/NOCT_Varpart_5seasons.png"), plot = varpartplot_noct, 
       dpi = 600, width = 6, height = 5)
```


