---
title: "JSDM_nocturnality_5seasons"
author: "Aimara Planillo"
date: "3/26/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **NOCTURNALITY JSDM model** with *5 seasons* 

Fall 2018, Spring 19, Fall 2019, Spring 20 (covid), Fall 20 (covid)

Run JSDM model of carnivore nocturnality (proportion of pictures taken at night: 9pm - 6am)
from citizen scientists camera traps 
in their gardens, using package from Ovaskainen/Tikhonov to obtain distributions and
species associations in Berlin.

Camera traps were set during 5 seasons, one month per season. 

* **Response variable**: 
  - *Nocturnality*: propotion of pictures of each species (independent events, at least 30 min apart) 
                    taken at night regarding the total (per camera trap)
    - Red Fox
    - Raccoon
    - Marten (stone marten + pine marten)

* **Explanatory variables**:
  - *Garden characteristics*:
    - compost: categorical (no, open, closed)
    - garden size: continuous (garden area measured citizens)
    - local tree cover: continuous (tree cover at gardens by citizens)
    - fence height: continuous (garden fence height by citizens)
  - *Urban characteristics*:
    - pop 100: continuous (human population density, n inhabitants, focal mean) 
    - imperv 100: continuous (impervious surface cover %, focal mean)
    - noise 100: continuous (noise levels day and night in dB(a), focal mean)
    - tree cover 100: continuous (tree cover %, focal mean)
    - distance_border: continuous (distance to city border, meters)
  - *Season*: categorical (fall, spring)
  - *covid*: categorical (yes, no)
  - *(Domestic) Cat* 

  


Data prepared by Julie Louvrier. Observations with Na in any explanatory variable 
have been previously removed. 

Urban characteristics variables scale: **100m resolution** (Focal means by Aimara Planillo)

* **Formula**:
~ garden_size + Local_tree_cover + fence_height + compost +
  pop_100 + imperv_100 + noise_100 + tree_cover_100 + d_cityB +
  season + covid
  
* **Random variable**:
- *NO*: spatial structure of sampling points
- Camera ID: not repeated

* Phylogeny = **NO**

* Traits: **NO** 
  
* **Model characteristics**
- 250000 samples
- Thinning: 20
- Burn-in: 10000
- n chains: 3
- Priors: uninformative


```{r packages and workspace}
#Packages and workspace  
source(paste0(getwd(), "/3_scripts/source_file_lib.R"))
source(paste0(getwd(), "/3_scripts/source_file_wd.R"))
```


## Load and clean data
```{r}
# load species nocturnal nocturnality data 
file_list <- list.files(data_wd, pattern = c("Noct"))
species_file <- sort(file_list, decreasing = TRUE)[1]

noct_tmp <- readRDS(file.path(data_wd, species_file))
head(noct_tmp)
str(noct_tmp) # 2485 obs. of  20 variables

summary(noct_tmp)

# get number of cameras per season
noct_tmp %>% 
  group_by(project_phase) %>% 
  summarise(n_cam = n_distinct(User_uid)) %>% 
  ungroup()  

# data divided into weekdays 0/1 (false/true). We pool it together for the whole month
# by summarizing the nbr_pictures_night column by species, user_uid and project_phase

noct_summary <- noct_tmp %>% 
  group_by(project_phase, species, User_uid) %>% 
  summarise(n_night = sum(nbr_pictures_night)) %>% 
  ungroup()  

noct_tmp[noct_tmp$User_uid == 73,]
noct_summary[noct_summary$User_uid == 73,]


# transform into a site (row) x species (column) matrix
head(noct_summary)
noct_sp_matrix <- noct_summary %>% 
  spread(key = species, value = n_night)
# change NA values for 0
noct_sp_matrix[is.na(noct_sp_matrix)] <- 0
nrow(noct_sp_matrix) # [1] 669



## Load the use data to get total number of pictures
use_data <- read.csv(paste0(data_wd, "/Use_envir_alldata_nodupl_noNa_mar21.csv"))
head(use_data)

# Get new data.frame with the proportions

noct_prop_tmp <- noct_sp_matrix %>% 
  left_join(use_data[,1:6], by = c("project_phase", "User_uid")) %>% 
  mutate(Cat.prop = Cat.x/Cat.y, 
         Fox.prop = Fox.x/Fox.y,
         Marten.prop = Marten.x/Marten.y,
         Raccoon.prop = Raccoon.x/Raccoon.y)
noct_prop_tmp

## load covariates in the appropiate format
# load envir variables
envir_file <- list.files(data_wd, pattern = "raster")
envcov <- readRDS(file.path(data_wd, envir_file))
head(envcov)
str(envcov)
summary(envcov)
nrow(envcov) # [1] 669

# add env covariates based on user id and project phase
# and add variables season and covid
noct_data <- noct_prop_tmp %>% 
  left_join(envcov, by = c("User_uid", "project_phase")) %>% 
  mutate(season = case_when(
    project_phase %in% c(1,3,5) ~ "Fall",
    project_phase %in% c(2,4) ~ "Spring"),
    covid = case_when(
    project_phase %in% c(1,2,3) ~ "No",
    project_phase %in% c(4,5) ~ "Yes"))

summary(noct_data)
head(as.data.frame(noct_data))

nrow(noct_data) #[1] 669
noct_data %>% 
  group_by(project_phase) %>% 
  summarise(n_cam = n_distinct(User_uid)) %>% 
  ungroup()

# write.csv(noct_data, paste0(data_wd, "/Nocturnality_envir_alldata_nodupl_noNa_mar21.csv"), row.names = FALSE)
# noct_data <- read.csv(paste0(data_wd, "/Nocturnality_envir_alldata_nodupl_noNa_mar21.csv"))
```
  project_phase n_cam
          <dbl> <int>
1             1   150
2             2   116
3             3   133
4             4   122
5             5   148


## Prepare data for Nocturnality JSDM model
```{r}
head(noct_data)
# response
noct_prop_matrix <- noct_data %>% 
  dplyr::select(Fox.prop, Marten.prop, Raccoon.prop) %>% 
  as.matrix()
head(noct_prop_matrix)

#####################################
## Change NA to Zeros for analyses
#####################################
# noct_prop_matrix[is.na(noct_prop_matrix)] <- 0


# covariates: select env variables 
covariates_noct <- noct_data %>%
  ungroup() %>% 
  dplyr::select(garden_size, Local_tree_cover, fence_height, compost, 
                pop_100, imperv_100, noise_100, tree_cover_100, distance_border, 
                season, covid, Cat.prop) %>% 
  # make all characters factors for running the model
  mutate(compost = as.factor(compost),
         season = as.factor(season), 
         covid = as.factor(covid),
         Cat.prop = ifelse(is.na(Cat.prop), 0, Cat.prop)) %>%  # Cat proportion NA transformed to zero, so the model works
  as.data.frame()


head(covariates_noct)
str(covariates_noct)
```


## Set up and Run the model
```{r}
# Study design and random effects (no spatial latent variable in this case, just camera id)
site.id <- as.factor(noct_data$User_uid)
studyDesign <- data.frame(site = site.id)
str(studyDesign)

rL <- HmscRandomLevel(units = studyDesign)
rL$s

# Define MCMC parameters
thin <- 20
samples <- 250000
transient <- 10000
nChains <- 3
verbose <- 1000

# samples <- 10000
# transient <- 500
# thin = 1


# Regression formula for environmental covariates
head(covariates_noct)
XFormula_noct = ~ garden_size + Local_tree_cover + fence_height + compost +
  pop_100 + imperv_100 + noise_100 + tree_cover_100 + distance_border +
  season + covid + Cat.prop


# BINOMIAL DISTRIBUTION: Untransformed data (Proportions)
## Model scales the data prior to running

# Fit the model
m <- Hmsc(Y = noct_prop_matrix, XData = covariates_noct, XFormula = XFormula_noct,
          studyDesign=studyDesign, ranLevels=list(site=rL),
          # TrData = NA, TrFormula = NA,
          distr = "probit") # for binomial data

# For repeatability 
set.seed(111)

# Run Markov Chains
# test
m <- sampleMcmc(m, thin = 1, samples = 50)

# Model run
m <- sampleMcmc(m, thin = thin, samples = samples, transient = transient,
               nChains = nChains, verbose = verbose,
               nParallel = 3) # 3 parallel processes 

# Set a name for the model
filename = paste0(nocturnality2_results_wd, "/CT_carnivores_nocturnality_5seasons_mar21_catexplanatory.rds")
 
#Save the model
saveRDS(m,file=filename) 
```


###########################
# Model Check and output
###########################

### Load the model
```{r load model}
filename = paste0(nocturnality2_results_wd, "/CT_carnivores_nocturnality_5seasons_mar21_catexplanatory.rds")
m <- readRDS(filename)
```

## Model convergence 

We evaluate MCMC convergence in terms of two kinds of parameters that we are especially interested in:
the species niches Beta, and the residual species associations Omega. 
The strength of phylogenetic signal rho and the influence of traits on species niches Gamma were not included in this model

Evaluate convergence: Effective sample size and gelman-rubin diagnostic (potencial reduction factor)
```{r model convergence}
mpost <- convertToCodaObject(m)

# Numerical output
ess.beta <- effectiveSize(mpost$Beta)
gd.beta <- gelman.diag(mpost$Beta, multivariate = FALSE)$psrf
ess.omega <- effectiveSize(mpost$Omega[[1]])
gd.omega <- gelman.diag(mpost$Omega[[1]], multivariate = FALSE)$psrf

convergence.names <- c("ess.beta", "ess.omega", "gd.beta", "gd.omega")
convergence.list <- list(ess.beta, ess.omega, gd.beta, gd.omega)
for (i in 1:length(convergence.names)){
  write.csv(convergence.list[[i]], paste0(nocturnality2_results_wd,
                                          "/", convergence.names[i], ".csv")) 
          # row.names = FALSE)
}

# Graphical output
png(paste0(nocturnality2_results_wd, "/CTcar_NOCT_5seasons_model_convergence_hist.png"), width = 800, height = 1000,
    pointsize = 20)
par(mfrow=c(2,2))
hist(ess.beta, main = "ess(beta)_CTcar_NOCT_5seasons")
hist(ess.omega, main = "ess(omega)_CTcar_NOCT_5seasons")
hist(gd.beta, main = "psrf(beta)_CTcar_NOCT_5seasons")
hist(gd.omega, main = "psrf(omega)_CTcar_NOCT_5seasons")
dev.off()

# Save plots of the chains
MCMCtrace(mpost$Beta, 
          pdf = TRUE, 
          open_pdf = FALSE,
          filename = "CTcar_NOCT_5seasons_MCMCtrace_beta",
          wd = nocturnality2_results_wd)
MCMCtrace(mpost$Omega[[1]], 
          pdf = TRUE, 
          open_pdf = FALSE,
          filename = "CTcar_NOCT_5seasons_MCMCtrace_omega",
          wd = nocturnality2_results_wd)

par(mfrow=c(1,1))

mean(ess.beta)
# [1] 492833.3
mean(gd.beta)
# [1] 1.000043
mean(ess.omega)
# [1] 100668.5
mean(gd.omega)
# [1] 1.001422

(autocorrBeta <- autocorr(mpost$Beta))
write.csv(autocorrBeta, paste0(nocturnality2_results_wd,
                                          "/autocorr_beta.csv"))

(autocorrOmega <- autocorr(mpost$Omega[[1]]))
write.csv(autocorrOmega, paste0(nocturnality2_results_wd,
                                          "/autocorr_omega.csv"))

plot(mpost$Beta)
plot(mpost$Omega[[1]])

saveRDS(mpost, paste0(nocturnality2_results_wd, "/mpost_coda_NOCT_5seasons.rds"))
# mpost <- readRDS(paste0(nocturnality2_results_wd, "/mpost_coda_NOCT_5seasons.rds"))
``` 


## Model Fit (R2)
```{r model fit}
# Explanatory R2. Get predictions for the observed values 
preds <- computePredictedValues(m, expected = TRUE)
saveRDS(preds, paste0(nocturnality2_results_wd, "/Preds_model_NOCT_5seasons.rds"))
# preds <- readRDS(paste0(nocturnality2_results_wd, "/Preds_model_NOCT_5seasons.rds"))

preds.values <- apply(abind(preds,along=3),c(1,2), median) # Median of the predictions
# write.csv(preds.values, paste0(nocturnality2_results_wd,
                                # "/Predicted_values_median_CTcar_NOCT_5seasons.csv"))
# preds.values <- read.csv(paste0(nocturnality2_results_wd,                                 "/Predicted_values_median_CTcar_NOCT_5seasons.csv"))

preds.values.mean <- apply(abind(preds, along = 3), c (1,2), mean) # Mean of the predictions
# write.csv(preds.values.mean, paste0(nocturnality2_results_wd,
                                    # "/Predicted_values_mean_CTcar_NOCT_5seasons.csv"))

# R2 with the built in function
modelr2.explanatory <- evaluateModelFit(hM = m, predY = preds)
modelr2.explanatory

r2.explanatory.sp <- cbind(as.data.frame(modelr2.explanatory), species = m$spNames)
r2.explanatory.sp
# write.csv(r2.explanatory.sp, paste0(nocturnality2_results_wd, "/NOCT_5seasons_explanatory_power.csv"),
#           row.names = FALSE)
```

$RMSE
[1] 0.3289908 0.2724539 0.2459968

$AUC
[1] 0.9922976 0.9010003 0.7994580

$TjurR2
[1] 0.15999553 0.06095295 0.03453756
```{r}
# AUC of the model
mean(modelr2.explanatory$AUC)
# [1] 0.8975853

# R2 of the model
mean(modelr2.explanatory$TjurR2)
# [1] 0.08516201

temp.r2 <- cbind.data.frame(r2 = as.numeric(modelr2.explanatory$AUC), 
                            species = as.character(m$spNames))
ggplot(data = temp.r2, aes(y=r2, x=species))+
  geom_point()
write.csv(modelr2.explanatory, paste0(nocturnality2_results_wd, "/CTcar_NOCT_5seasons_explanatory_R2_default.csv"), 
          row.names = FALSE)


# R2 Manually comparing observed vs predicted
R2.sp <- matrix(NA, m$ns, 1)
for (i in 1:m$ns) {
  R2.sp[i, ] <- cor(preds.values.mean[, i],m$Y[, i], use  = "pairwise.complete.obs")^2
}

mean(R2.sp, na.rm=TRUE)
# [1] 0.147485

# Plot of the default R2
# Plot of the default R2
ggplot(data = as.data.frame(modelr2.explanatory$SR2), aes(y=modelr2.explanatory$TjurR2, x=temp.r2$species))+
  geom_point() +
  xlab("Species") +
  ylab("R2 for each species") +
  ggtitle(paste0("Urban Mammals - Default SR2 species \n R2 = ", 
                   round(mean(modelr2.explanatory$SR2, na.rm = TRUE), 2)))
ggsave(paste0(nocturnality2_results_wd, "/Plot_R2_species_default_NOCT_5seasons.png"))


# Plot of the manual R2
ggplot(data = as.data.frame(R2.sp), aes(y=V1, x=temp.r2$species))+
  geom_point() +
  xlab("Species") +
  ylab("R2 for each species") +
  ggtitle(paste0("Urban Mammals - Obs vs pred R2 species \n R2 = ", 
                   round(mean(R2.sp, na.rm = TRUE), 2)))
ggsave(paste0(nocturnality2_results_wd, "/Plot_R2_species_manual_NOCT_5seasons.png"))
```

```{r site R2}
R2.site <- matrix(NA, m$ny, 1)
for (i in 1:m$ny) {
  R2.site[i, ] <- cor(preds.values.mean[i, ], m$Y[i, ])^2
}
mean(R2.site, na.rm = TRUE)
# [1] 0.5628711


ggplot(data = as.data.frame(R2.site), aes(y=V1, x=seq(1, nrow(R2.site), by =1)))+
  geom_point() +
  xlab("Site index") +
  ylab("R2 for each species") +
  ggtitle(paste0("Urban Mammals - Obs vs pred R2 sites \n R2 = ", 
                   round(mean(R2.site, na.rm = TRUE), 2)))
ggsave(paste0(nocturnality2_results_wd, "/Plot_R2_sites_manual_NOCT_5seasons.png"))


# prevalence and r2
ggplot(data = as.data.frame(R2.sp), aes(y=V1, x=colSums(m$Y) / m$ny))+
  geom_point() +
  xlab("Proportion of Sites") +
  ylab("R2 for each species") +
  ggtitle(paste0("Urban Mammals - Explanatory R2: proportion of sites present\n R2 = ", 
                   round(mean(R2.site, na.rm = TRUE), 2)))
ggsave(paste0(nocturnality2_results_wd, "/Plot_R2_prevalence_manual_NOCT_5seasons.png"))


# compare predicted and observed col sums (one data point is a species)
png(paste0(nocturnality2_results_wd, '/Plot_Obs_vs_Pred_sp_NOCT_5seasons.png'))
plot(colSums(preds.values)~colSums(m$Y, na.rm = TRUE),
     main = paste0("Urban Mammals", " - Observed vs Predicted Species presences \n Mean R2 = ", round(mean(R2.sp, na.rm = TRUE), 2)),
     xlab = "n observed sites",
     ylab = "n predicted sites",
     pch = 16)
abline(0,1, col = "red", 
       lty = 4,
       lwd = 1)
dev.off()
```

## Posterior predictive check 

```{r}
# Select 50 first predictions
# preds_tmp <- preds[, ,1:50]
# saveRDS(preds_tmp, paste0(nocturnality2_results_wd, "/preds_ppc_NOCT_5seasons.rds"))
preds_tmp <- readRDS(paste0(nocturnality2_results_wd, "/preds_ppc_NOCT_5seasons.rds"))
head(preds_tmp[,,1])

noct_data <- read.csv(paste0(data_wd, "/Nocturnality_envir_alldata_nodupl_noNa_mar21.csv"))
head(noct_data)
# response
noct_prop_matrix <- noct_data %>% 
  dplyr::select(Fox.prop, Marten.prop, Raccoon.prop) 

# change NA to 0
noct_prop_matrix[is.na(noct_prop_matrix)] <- 0
head(noct_prop_matrix)


### red fox
# Extract observed y
y_fox <- as.vector(noct_prop_matrix$Fox.prop)

# extract 50 predicted y
test <- data.frame(Species = rep("Red_fox", nrow(preds_tmp[,,1])))
for(i in 1:dim(preds_tmp)[3]){
  x <- as.vector(preds_tmp[,,i][,"Fox.prop"])
  test[,ncol(test)+1] <- x
  colnames(test)[ncol(test)] <- paste0("fox", i)
}
ypred_fox <- t(as.matrix(test[,-1]))

# Run function
ppc_fox <- pp_check(y_fox, ypred_fox, ppc_dens_overlay) +
  ggtitle("PPC - Fox nocturnality")
ggsave(plot = ppc_fox, filename = paste0(plots_wd, "/ppc_NOCT_fox.png"), 
       dpi = 600, width = 9, height = 5.8)

### raccoon
# Extract observed y
y_rac <- as.vector(noct_prop_matrix$Raccoon.prop)

# extract 50 predicted y
test <- data.frame(Species = rep("Raccoon", nrow(preds_tmp[,,1])))
for(i in 1:dim(preds_tmp)[3]){
  x <- as.vector(preds_tmp[,,i][,"Raccoon.prop"])
  test[,ncol(test)+1] <- x
  colnames(test)[ncol(test)] <- paste0("raccoon", i)
}
ypred_raccoon <- t(as.matrix(test[,-1]))

# Run function
ppc_rac <- pp_check(y_rac, ypred_raccoon, ppc_dens_overlay) +
  ggtitle("PPC - Raccoon nocturnality")
ggsave(plot = ppc_rac, filename = paste0(plots_wd, "/ppc_NOCT_raccoon.png"), 
       dpi = 600, width = 9, height = 5.8)


### marten
# Extract observed y
y_marten <- as.vector(noct_prop_matrix$Marten.prop)

# extract 50 predicted y
test <- data.frame(Species = rep("Marten", nrow(preds_tmp[,,1])))
for(i in 1:dim(preds_tmp)[3]){
  x <- as.vector(preds_tmp[,,i][,"Marten.prop"])
  test[,ncol(test)+1] <- x
  colnames(test)[ncol(test)] <- paste0("marten", i)
}
ypred_marten <- t(as.matrix(test[,-1]))

# Run function
ppc_mart <- pp_check(y_marten, ypred_marten, ppc_dens_overlay) +
  ggtitle("PPC - Marten nocturnality")
ggsave(plot = ppc_mart, filename = paste0(plots_wd, "/ppc_NOCT_marten.png"), 
       dpi = 600, width = 9, height = 5.8)
```


## Beta values

```{r betas}
Beta.results <- as.data.frame(MCMCsummary(mpost$Beta))
write.csv(Beta.results, paste0(nocturnality2_results_wd, "/CTcar_NOCT_5seasons_beta_coeffients.csv"), row.names = TRUE)
# Default beta plot in Hmsc package
postBeta <- getPostEstimate(m, parName = "Beta")
saveRDS(postBeta, file=paste0(nocturnality2_results_wd, "/postBeta_5seasons.rds"))

png(paste0(nocturnality2_results_wd, "/CTcar_NOCT_5seasons_default_betaplot_support95.png"))
plotBeta(m, post = postBeta, param = "Support", supportLevel = 0.95)
dev.off()
  
png(paste0(nocturnality2_results_wd, "/CTcar_NOCT_5seasons_default_betaplot_support75.png"))
plotBeta(m, post = postBeta, param = "Support", supportLevel = 0.75)
dev.off()

# my plots
# Coef plot for betas for each species
pdf(paste0(nocturnality2_results_wd, "/CTcar_NOCT_5seasons_beta_coef_plots.pdf"))
MCMCplot(mpost$Beta, 
           ref_ovl = TRUE,
           rank = T,
           xlab = 'ESTIMATE',
           sz_labels = 0.3,
           sz_med = 1,
           sz_thick = 3,
           sz_thin = 1,
           sz_ax = 1,
           sz_main_txt = 1)
dev.off()


# Print a plot for each predictor
n.cov <- length(m$covNames) # Number of covariates without the intercept
  var.code <- vector()
  for (i in 1:n.cov){
    var.code[i] <- paste0("C", i)
  }
  
var.name <- as.vector(m$covNames[1:n.cov])
predictors <- as.data.frame(cbind(var.code, var.name))
  
for (i in 1:nrow(predictors)){
    png(paste0(nocturnality2_results_wd, "/Betas_covariates_coef_plot_", 
               var.name[i], "_5seasons.png"), width = 5, 
        height = 8, units = "in", res = 300, pointsize = 16)
    MCMCplot(mpost$Beta,
             params = predictors[i,1],
             ISB = FALSE,
             ref_ovl = TRUE,
             rank = FALSE,
             xlab = 'ESTIMATE',
             main = predictors[i,2],
             sz_labels = 0.5,
             sz_med = 1,
             sz_thick = 1,
             sz_thin = 1,
             sz_ax = 1,
             sz_main_txt = 1)
    dev.off()
}

```

## Extract beta values for manual plotting

From the code object, load the model and then divide the data as one dataset per species, 
extract the posterior summaries and give the proper names to the variables

```{r}
# coda object (model output)
# mpost <- readRDS(paste0(nocturnality2_results_wd, "/mpost_coda_NOCT_5seasons.rds"))

# betas (coefficients) for each species
head(mpost$Beta)

# Get species data
mpost.beta.fox <- mpost$Beta[,grep("Fox", colnames(mpost$Beta[[1]]))]
mpost.beta.raccoon <- mpost$Beta[,grep("Raccoon", colnames(mpost$Beta[[1]]))]
mpost.beta.marten <- mpost$Beta[,grep("Marten", colnames(mpost$Beta[[1]]))]

head(mpost.beta.marten)
summary(mpost.beta.marten)

### Rearrange data to new data frame for plotting
colnames(mpost.beta.fox[[1]])

# new names for the explanatory variables
my_variables <- c("Intercept", "Garden_size", "Local_tree_cover", "Fence_height",  
                  "No_compost", "Open_compost", 
                  "Human_population", "Impervious_surface", "Noise", "Tree_cover", 
                  "Dist_B", "Spring", "Covid", "Cat")

#rename columns in betas
for (i in 1:length(mpost.beta.fox)){
  colnames(mpost.beta.fox[[i]]) <- my_variables
}
for (i in 1:length(mpost.beta.raccoon)){
  colnames(mpost.beta.raccoon[[i]]) <- my_variables
}
for (i in 1:length(mpost.beta.marten)){
  colnames(mpost.beta.marten[[i]]) <- my_variables
}

# extract values to plot
# summary(mpost.beta.fox)$statistics
# summary(mpost.beta.fox)$quantiles

# Put model estimates into temporary data.frames. Add variable "Species" for plotting
model1Frame <- data.frame(Variable = my_variables,
                          Coefficient = summary(mpost.beta.fox)$statistics[,1],
                          CI_low = summary(mpost.beta.fox)$quantiles[,1],
                          Q_25 = summary(mpost.beta.fox)$quantiles[, 2],
                          Q_50 = summary(mpost.beta.fox)$quantiles[,3],
                          Q_75 = summary(mpost.beta.fox)$quantiles[, 4],
                          CI_high = summary(mpost.beta.fox)$quantiles[,5],
                          Species = "Fox") 

model2Frame <- data.frame(Variable = my_variables,
                          Coefficient = summary(mpost.beta.raccoon)$statistics[,1],
                          CI_low = summary(mpost.beta.raccoon)$quantiles[,1],
                          Q_25 = summary(mpost.beta.raccoon)$quantiles[, 2],
                          Q_50 = summary(mpost.beta.raccoon)$quantiles[,3],
                          Q_75 = summary(mpost.beta.raccoon)$quantiles[, 4],
                          CI_high = summary(mpost.beta.raccoon)$quantiles[,5],
                          Species = "Raccoon")

model3Frame <- data.frame(Variable = my_variables,
                          Coefficient = summary(mpost.beta.marten)$statistics[,1],
                          CI_low = summary(mpost.beta.marten)$quantiles[,1],
                          Q_25 = summary(mpost.beta.marten)$quantiles[, 2],
                          Q_50 = summary(mpost.beta.marten)$quantiles[,3],
                          Q_75 = summary(mpost.beta.marten)$quantiles[, 4],
                          CI_high = summary(mpost.beta.marten)$quantiles[,5],
                          Species = "Marten")


# Combine these data.frames
allModelFrame <- data.frame(rbind(model1Frame, model2Frame, model3Frame)) 

# Relevel factors so they are plotted in the desired order
allModelFrame$Variable <- factor(allModelFrame$Variable, levels = rev(my_variables))
allModelFrame$Species <- factor(allModelFrame$Species,levels = c("Raccoon", "Fox", "Marten"))
summary(allModelFrame)
write.csv(allModelFrame, paste0(nocturnality2_results_wd, "/NOCT_all_5seasons_ModelFrame.csv"), row.names = FALSE)
```


## Speceis co-occurrences 

We do it throuch species associations in residual random variance

```{r sp associations}
OmegaCor <- computeAssociations(m)
class(OmegaCor)
saveRDS(OmegaCor, file=paste0(nocturnality2_results_wd, "/OmegaCor_NOCT_5seasons.rds"))

OmegaCor[[1]]$mean
OmegaCor[[1]]$support

# Default plot in Hmsc package
supportLevel <- 0.95

toPlot <- ((OmegaCor[[1]]$support > supportLevel)
           + (OmegaCor[[1]]$support < (1 - supportLevel)) > 0) * OmegaCor[[1]]$mean
png(paste0(nocturnality2_results_wd , "/CTcar_NOCT_5seasons_default_omegaplot95.png"))
corrplot(toPlot, method = "color", 
         col = colorRampPalette(c("blue", "white", "red"))(200),
         title = paste0("random effect level: ", m$rLNames[1]), 
         mar = c(0,0,1,0))
dev.off()

supportLevel <- 0.75
toPlot <- ((OmegaCor[[1]]$support > supportLevel)
           + (OmegaCor[[1]]$support < (1 - supportLevel)) > 0) * OmegaCor[[1]]$mean
png(paste0(nocturnality2_results_wd, "/CTcar_NOCT_5seasons_default_omegaplot75.png"))
corrplot(toPlot, method = "color", 
         col = colorRampPalette(c("blue", "white", "red"))(200),
         title = paste0("random effect level: ", m$rLNames[1]), 
         mar = c(0,0,1,0))
dev.off()

par(mar = c (5,5,4,5))
```


```{r save associations}
assoc.mean <- melt(OmegaCor[[1]]$mean)
assoc.support <- melt(OmegaCor[[1]]$support)

nrow(assoc.mean); nrow(assoc.support)

associations <- cbind.data.frame(assoc.mean, support = assoc.support$value)
colnames(associations) <- c("species1", "species2", "mean", "support")

associations

write.csv(associations, paste0(nocturnality2_results_wd, "/UrbanMammals_associations_NOCT_5seasons.csv"), row.names = FALSE)
```

## Variance partitioning

The order of the variables, if they are continuous, is 
1. intercept(this can be in any group)
2. first variable
3. second variable
ETC.

The formulas we used for running the models area: 
XFormula =  ~ compost + garden_size + Local_tree_cover + fence_height +
  pop_100 + imperv_100 + noise_100 + tree_cover_100 + d_cityB + season + covid + Cat

```{r variance partitioning}
# design matrix
head(m$X)

# Total variance explained by hte model can be partition into the contributions
# of each fixed effect (or group) and random effect
# intercept can go in any group. Here in the first to simplify
# Groups: season, garden, landscape, cats
VP <- computeVariancePartitioning(m, group = c(1,1,1,1,1,1, 2,2,2,2,2 ,3,4,5), groupnames = c("urban", "garden", "season", "covid", "cats"))

# Save the Variance partitioning info
VP$vals
VP$R2T

saveRDS(VP, file = paste0(nocturnality2_results_wd, "/Varpart_NOCT_5seasons.rds"))

VP.table <- as.data.frame(VP$vals) 
VP.table
write.csv(VP.table, paste0(nocturnality2_results_wd, "/Varpart_values_NOCT_5seasons.csv"))


# plot var part
png(paste0(nocturnality2_results_wd, "/CTcar_Carnivores_NOCT_5seasons_default_VP.png"), 
    width = 800)
plotVariancePartitioning(m, VP = VP, las = 2, cex.names = 0.8)
title(main = "\n \nNOCT INTENSITY Urban Mammals")
dev.off()
```


## Predicted responses 95CI

### Example full community
```{r}
m$XFormula
head(m$X)

Gradient.season <- constructGradient(m, focalVariable = "season")
predY <- predict(m, XData = Gradient.season$XDataNew, studyDesign = Gradient.season$studyDesignNew, 
                 ranLevels = Gradient.season$rLNew, expected = FALSE)

# Summed response to season
plotGradient(m, Gradient.season, pred=predY, measure="S", las=1,
             showData = TRUE, main='Species richness (measure="S")')

# Species 3
plotGradient(m, Gradient.season, pred=predY, measure="Y", index=3, las=1,
             showData = TRUE, main='Focal species occurrence (measure="Y", species = 3)')
# Community-weighted mean values of traits
# plotGradient(m, Gradient.season, pred=predY, measure="T", index=2, las=1,
#              showData = TRUE, main='Mean trait value (measure="T")')


# Summed response to cat
Gradient.tree <- constructGradient(m, focalVariable = "tree_cover_100", non.focalVariables = 1)
predY.tree <- predict(m, Gradient=Gradient.tree)
plotGradient(m, Gradient.tree, pred=predY.tree, measure="Y", index = 1, 
             showData = TRUE, main='Response to tree cover')
```

### Predicted responses 95CI by species

```{r}

```



